Predicting Diamond Pricing: A Generalized Linear Model Analysis

### 2024-12-04 paper/paper.qmd
Update Ideal Methodology and Ideal Survey

@@

>>>>

This methodology draws upon existing literature to guide its framework. For example, @verbeek2017 points out the importance of stratified sampling and multi-wave data collection in ensuring representative and reliable datasets in market studies. Similarly, @syverson2019 emphasizes the role of data standardization and cleaning in enhancing the accuracy of econometric modeling. These references underpin the methodological rigor employed in this study, ensuring that it aligns with established best practices in empirical research.

@@

The survey aims to find consumer behavior, preferences, and perceptions related to diamonds. The survey design incorporates both structured and open-ended questions to balance quantitative rigor with qualitative ideas. Questions address demographic characteristics, behavioral patterns, perceptions of diamond characteristics, and satisfaction with previous purchases.

This survey design is informed by prior research. For example, @dhaliwal2020 analyzes the importance of open-ended questions in uncovering consumer preferences in the luxury market. In addition, @wilson2018 recommend a mix of Likert-scale and multiple-choice questions to enhance respondent engagement and reduce fatigue. These studies guide the development of a good questionnaire that maximizes data quality while ensuring respondent satisfaction.
